\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}


% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItemSmall}[2]{
	\item[]
	\small{
		\textbf{#1}{: #2 \vspace{-2pt}}
	}
}

\newcommand{\resumeItem}[2]{
  \item
  \small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubItemSmall}[2]{\resumeItemSmall{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}





%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
	
	
	
%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/jasonmren/}{\Large Jason Matthew Ren}} & \href{mailto:jasonren@wustl.edu}{jasonren@wustl.edu}\\
  \href{https://www.linkedin.com/in/jasonmren/}{https://www.linkedin.com/in/jasonmren/} & +1-610-203-2179 \\
  \href{https://github.com/jasonren5}{https://github.com/jasonren5}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Washington University in St. Louis}{St. Louis, MO}
      {Sophomore Computer Science Student;  GPA: 3.22}{Aug. 2017 -- May 2021 (expected)}
      \resumeItemListStart
      	\resumeItem{Teaching Assistant for:}{}
      		\begin{itemize}
      			\item CSE132: Computer Science II (Spring 2019)
      			\item CSE330: Rapid Prototyping and Development (Spring 2019)
      		\end{itemize}
      \resumeItemListEnd
    \resumeSubheading
      {Great Valley High School}{Malvern, PA}
      {SAT: 2360}{Aug. 2013 - June 2017}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  	\resumeSubheading {Institute for Public Health at Washington University}{St. Louis, MO}{Data Analyst}
  	{Aug 2018 - Present}
  	\resumeItemListStart
  		\resumeItem{Scripting}{Cleaned, standardized, and merged trauma center visitation data from local St. Louis hospitals with Python's regular expression and .csv packages, and created a patient identification system utilizing hash and soundex codes.}
  		\resumeItem{Data Visualization}{Created maps of the Saint Louis region with Tableau depicting social statistics such as race distributions for United Way of Greater Saint Louis in order to determine areas most in need of funding and aid.}
  		\resumeItem{Data Cleaning}{Wrote scripts in Python using the BeautifulSoup library to clean, re-format, and visualize violent crime incident data from St. Louis County Police.}
  	\resumeItemListEnd
  
  	\resumeSubheading {Lavner Camps and Programs}{Narberth, PA}{Technology Instructor and IT Technician}
  	{May 2018 - Aug. 2018}
  	\resumeItemListStart
  		\resumeItem{Technology Instructor}{Taught kids aged 7 to 12 the basics of programming with Python and Java.}
  		\resumeItem{IT Technician}{Prepared computer and device inventory to be distributed to summer camp locations. Wrote scripts to optimize work flow and increase efficiency of team.}
  	\resumeItemListEnd
  		
    \resumeSubheading
      {PrimBio Research Institute LLC.}{Exton, PA}
      {Software Intern}{June 2016 - Aug. 2016}
      \resumeItemListStart
        \resumeItem{Python}
          {Wrote a script in Python that converted data from .fastq filetype to .fasta and subsequently compressed said data using 7zip with the goal of bettering workflow.}
        \resumeItem{Data Visualization}
          {Analyzed and formatted raw cell count data of various bacteria within samples into corresponding taxonomic ranks in Microsoft Excel for customers.}
      	\resumeItem{Website Development}
      	  {Refined and simplified navigation of the website, and also brought the website up to date with current information and services.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  
%-----Personal-Projects-------  
\section{Personal Projects}

	\resumeSubHeadingListStart
		\resumeSubItemSmall{1001monkeys}{Node.JS web app with a React.JS front-end in which users write a new book each day together by submitting short blurbs, and then voting on the next blurb to be added to the book.}
		\resumeSubItemSmall{ren-soundex}{Python 3 package that implements the Soundex algorithm, which codes words into numbers in order to correct for spelling mistakes.}
		\resumeSubItemSmall{chat-server}{Node.JS web app instant messaging service, utilizing Socket.IO for client-server interaction.}
		\resumeSubItemSmall{calendar}{Cloud based calendar service hosted on an Amazon EC2 server using Apache. Created using JQuery for front-end, and a PHP-based backend interacting with a MySQL database on an Amazon EC2 server.}
		\resumeSubItemSmall{rpg-clicker-game}{An incremental RPG game created with the Bootstrap HTML framework and JQuery.}
	\resumeSubHeadingListEnd
	
%--------PROGRAMMING SKILLS------------
\section{Skills}
\resumeSubHeadingListStart
\item[]{
	\textbf{Languages}{: Python 3, Java, PHP, MySQL, C\#, C, HTML, JavaScript (and JQuery), Node.JS, CSS, LaTeX}
	\hfill
	\\
	\textbf{Technologies}{: Apache, Amazon AWS/EC2, Linux, Unity, Git, Microsoft Office}
}
\resumeSubHeadingListEnd
%-------------------------------------------

%-----Additional Information----------
\section{Additional Information}

	\resumeSubHeadingListStart
		\resumeSubItemSmall{Member of Alpha Delta Phi}
		{PR Manager for Alpha Delta Phi's Eliot Chapter.}
		\resumeSubItemSmall{Member of Campus Y}{Volunteer at Clowder House Foundation, a local St. Louis animal shelter.}
	\resumeSubHeadingListEnd
	
\end{document}

%Wow, you've reached the bottom of my resume. Thanks for reading!