\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}


% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}





%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
	
	
	
%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://www.linkedin.com/in/jasonmren/}{\Large Jason Matthew Ren}} & \href{mailto:jasonren@wustl.edu}{jasonren@wustl.edu}\\
  \href{https://www.linkedin.com/in/jasonmren/}{https://www.linkedin.com/in/jasonmren/} & +1-610-203-2179 \\
  \href{https://github.com/jasonren5}{https://github.com/jasonren5}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Washington University in St. Louis}{St. Louis, MO}
      {Sophomore Computer Science Student;  GPA: 3.22}{Aug. 2017 -- May 2021 (expected)}
      \resumeItemListStart
      	\resumeItem{Relevant Coursework}{}
      		\begin{itemize}
      			\item Logic and Discrete Math
      			\item Web Development
      			\item Data Structures and Algorithms
      			\item Introduction to Digital Logic and Computer Design
      			\item Rapid Prototyping and Development
      		\end{itemize}
      \resumeItemListEnd
    \resumeSubheading
      {Great Valley High School}{Malvern, PA}
      {SAT: 2360 (800CR/800M/760W)}{Aug. 2013 - June 2017}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  	\resumeSubheading {Washington University Institute for Public Health}{St. Louis, MO}{Data Analyst}
  	{Aug 2018 - Present}
  	\resumeItemListStart
  		\resumeItem{Database work}{Standardize and clean clinical datasets pulled from electronic medical record systems through the use of REDCap API's and Python.}
  		\resumeItem{Modeling}{Help design a strategy and plan to merge clinical and police data on violent injuries.}
  	\resumeItemListEnd
  
  	\resumeSubheading {Lavner Camps and Programs}{Narberth, PA}{Technology Instructor and IT Technician}
  	{May 2018 - Aug. 2018}
  	\resumeItemListStart
  		\resumeItem{Technology Instructor}{Taught kids aged 7 to 12 the basics of programming with Python and Java. Was responsible for leading classroom instruction, as well as camper safety.}
  		\resumeItem{IT Technician}{In an office setting, installed various pieces of software on hundreds of computers to be distributed to multiple camp locations. Wrote scripts to automate the process.}
  	\resumeItemListEnd
  		
    \resumeSubheading
      {PrimBio Research Institute LLC.}{Exton, PA}
      {Software Intern}{June 2016 - Aug. 2016}
      \resumeItemListStart
        \resumeItem{Python}
          {Added to and edited a script written in Python that converted data from .fastq filetype to .fasta and subsequently compressed said data using 7zip.}
        \resumeItem{Microsoft Excel}
          {Analyzed and formatted raw cell count data of various bacteria within samples into corresponding taxonomic ranks for customer presentation.}
      	\resumeItem{Website Development}
      	  {Refined and simplified navigation of the website, and also updated company information and services.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
  
%-----Personal-Projects-------  
\section{Personal Projects}

	\resumeSubHeadingListStart
		\resumeSubItem{rpg-clicker-game}{An incremental RPG game written in HTML (using Bootstrap), and JavaScript and JQuery.}
		\resumeSubItem{personal-website}{A personal website written in HTML (using Bootstrap) and CSS.}
		\resumeSubItem{caesar-cipher}{A short Python program written to educate young teens on programming principles and basic encryption.}
		\resumeSubItem{resume}{This resume, which is typeset in LaTeX!}

		
	\resumeSubHeadingListEnd
%------------Work-------------
%\section{Volunteer Work}
%	\resumeSubHeadingListStart
%		\resumeSubheading{Paoli Hospital}{Paoli, PA}{Patient Transport}{Summer 2015 and Summer 2016}
%			\resumeItemListStart
%				\resumeItem{Duties}
%					{Transported patients to and from patient rooms and various departments of the hospital, including surgery and ER either independently or in pairs, as well as discharging patients from the hospital. Sanitized hospital equipment during downtime.}
%			\resumeItemListEnd
%	
%	\resumeSubHeadingListEnd  

\section{Additional Information}

	\resumeSubHeadingListStart
		\resumeSubItem{Member of Alpha Delta Phi}
		{Current PR Manager for Alpha Delta Phi's Washington University Chapter.}
		\resumeSubItem{Member of Campus Y}{Volunteer at local St. Louis animal shelter.}
		\resumeSubItem{National Merit Finalist}
		{1500/1520 on October 2015 PSAT.}
		\resumeSubItem{Interests and Hobbies}
		{Philadelphia Eagles, data science, web-application development, violin performance, underground music, mechanical keyboards, video game development,  writing, photography.}

	\resumeSubHeadingListEnd
	
%--------PROGRAMMING SKILLS------------
%\section{Skills}
% \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Python (2.x and 3.x), C\#, Java, C, HTML, JavaScript, CSS, LaTeX}
%      \hfill
%      \\
%      \textbf{Technologies}{: Arduino, Unity, Slack, Git, Google App Suite, Microsoft Office}
%    }
%  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}

%Wow, you've reached the bottom of my resume. Thanks for reading!